Assessing Virulence by MCG

### 2017-06-29 doc/RMD/MCG-virulence.Rmd
add Tukey Test

## AMOVA

The default AMOVA in R sets contrasts as `contrast.treatment`, which compares
everything to the first factor, considered the treatment. Since we are
interested in whether or not there IS a difference between samples, this will
be sufficient.

```{r amova}
AMOVA <- aov(Severity ~ MCG, data = top_mcg)
AMOVA
summary(AMOVA)
```

There appears to be a significant effect at p = `r formatC(broom::tidy(AMOVA)$p.value[1])`.

>>>>

## ANOVA

The default ANOVA in R sets contrasts as `contrast.treatment`, which compares
everything to the first factor, considered the treatment. Since we are
interested in whether or not there IS a difference between samples, this will
be sufficient.

After the ANOVA, we performed a Tukey's Honest Significant Difference test to
see exactly what groups these fell into.

```{r anova, fig.width = 4, fig.height = 8}
ANOVA <- aov(Severity ~ MCG, data = top_mcg)
ANOVA
summary(ANOVA)
plot(TukeyHSD(ANOVA), las = 2)
agricolae::HSD.test(ANOVA, "MCG")$groups
```

There appears to be a significant effect at p = `r formatC(broom::tidy(ANOVA)$p.value[1])`.
